---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```
# ExtracellularEnzymeActivity_Data_Prep

<!-- badges: start -->
<!-- badges: end -->

The goal of ExtracellularEnzymeActivity_Data_Prep is to import/clean and explore FLEE lab Extracellular Enzyme Activity (EEA) data from microplate readings. The data from the reader must be saved as .xlsx files, named after the sample as SampleDayNumber_replicate_factor (ex: S09_B_C3 in the sample case represents 9th day sample, replicate B, factor level "C3") within the "data" folder.

```{r, message = FALSE, warning = FALSE}
library(data.table)
library(readxl)
library(purrr)
library(ggplot2)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

Get the file names as sample names and the functions
```{r}
BiblioDir = list.dirs(path = "data", full.names =T, recursive = F)
paths = list.files(BiblioDir, full.names = T)
source("R/functions.R")
source("R/plotting_functions.R")
```
Read the enzyme activity data from the plate readings 
```{r, warning = FALSE}
Gly = enzyme_as_data_table(paths, func=read_glu)
Xyl = enzyme_as_data_table(paths, func=read_xyl)
Cbh = enzyme_as_data_table(paths, func=read_Cbh)
```

Data is stored as lists for ease of use when the sample number is high
```{r}
list_data = map(list(Gly=Gly, Xyl=Xyl, Cbh=Cbh), convert_to_numeric)
list_data = map(list_data, calculate_mean)
```

Calculate each enzyme ratio separately. Check the functions folder for more details
```{r}
ER_xyl_glu = calculate_xyl_gly (list_data)
ER_glu_xyl_cbh = calculate_glu.xyl_cbh (list_data)
```
Convert the NaN and Inf values to 0 since these are all below the detection limit values due to the negative data in the measurements. 
``` {r}
list = list(ER_xyl_glu, ER_glu_xyl_cbh)
ER_data = Reduce(function (...)  merge(..., by="sample"), list) 

ER_data[is.nan.data.frame(ER_data)] <- 0
ER_data[is.inf.data.frame(ER_data)] <- 0
```
Cleaning and appropriately naming the factors
``` {r, echo = FALSE}
ER_data[,c("sample_date", "replicate", "col_no") := tstrsplit(sample, "_")]
ER_data$sample_date = factor(ER_data$sample_date,
                           levels = c("S09", "S13", "S16", "S19"),
                           labels = c("Day0", "Day3", "Day10", "Day17")) #Convert the sample date to days as a factor for ease in plotting
ER_data$col_no = factor(ER_data$col_no,
                                 levels = c("C1", "C2"),
                                 labels = c("Col1", "Col2"))
```
``` {r}
ER_data = set_coloring_column(ER_data)
ggplot(ER_data, mapping = aes(x=sample_date, y = xyl_gly.median))+
  facet_grid(~col_no, labeller = as_labeller(col_names))+
  geom_boxplot(mapping = aes(fill = highlight, col = highlight))+
  fill_col_no2 () + color_col_no2() +
  theme_boxplot() +
  ylab("Xyl/Glu")
```